Read redundancies

### 2015-12-01 code/05_read_redundancy.Rmd
presentation figures

@@

>>>>

inv <- dplyr::data_frame(net = unique(node_redundancy$net) %>% as.character(),
												 inv = grepl("2", net) | grepl("4", net)) %>% 
	dplyr::mutate(site = rep(c("BAT", "FRA", "MED", "FAR", "MIQ", "SEL"), each =2),
								invader = rep(c("car", "op", "car", "op"),  c(2, 2, 4, 4)))

nr <- node_redundancy %>%
	dplyr::mutate(type = interaction(type, keep)) %>%
	dplyr::group_by(net, type, robustness) %>%
	dplyr::summarise(n = n()) %>%
	tidyr::spread(robustness, n) %>%
	dplyr::mutate(critical = replace(critical, is.na(critical), 0),
								ordinary = replace(ordinary, is.na(ordinary), 0)) %>%
	dplyr::filter(type == "weight.A") %>%
	dplyr::inner_join(inv)

points <- 
	rbind(c(1, 0, 0, 100), 
				c(2, 100, 0, 0),
				c(3, 0, 100, 0),
				c(4, 100/3, 100/3, 100/3),
				c(5, 50, 0, 50), 
				c(6, 0, 50, 50),
				c(7, 50, 50, 0)) %>%
	data.frame() %>%
	`colnames<-`(c("id", "o", "c", "r")) %T>% {
		ggtern(data = ., aes(o, c, r)) +
			geom_text(aes(label = id))
	}

polygons <- 
	rbind(c(1, 1),
				c(1, 5),
				c(1, 4),
				c(1, 6),
				c(2, 2),
				c(2, 7),
				c(2, 4),
				c(2, 5),
				c(3, 3),
				c(3, 6),
				c(3, 4),
				c(3, 7)) %>%
	data.frame() %>%
	`colnames<-`(c("lab", "id")) %>%
	inner_join(points)

pdf("./presentation_figures/tern_net_poster.pdf", width = 14.5, height = 5.5)
ggplot() + 
		geom_polygon(data = polygons, aes(x = o, y = c, z = r,  fill = as.factor(lab)), colour = "black", size = 1) +
	geom_point(data = nr, aes(x = ordinary, z = redundant, y = critical), size = 8, shape = 21, fill = "white") +
	coord_tern()	 + scale_fill_manual(values = c("#4daf4a", "#377eb8", "#e41a1c")) +
	theme(text = element_blank())
dev.off()

pdf("./presentation_figures/tern_net_pres.pdf", width = 8, height = 5.5)
ggplot() + 
		geom_polygon(data = polygons, aes(x = o, z = c, y = r,  fill = as.factor(lab)), colour = "black", size = 1) +
	geom_point(data = nr, aes(x = ordinary, y = redundant, z = critical), size = 5, shape = 21, fill = "white", alpha = 0.9) +
	coord_tern()	 + scale_fill_manual(values = c("#4daf4a", "#377eb8", "#e41a1c")) +
	theme(text = element_blank())
dev.off()
```

@@

# Link redundancy

```{r}
folder <- "./data/redundancy/edge/"

link_redundancy <- list.files(folder, full.names = TRUE) %>%
	plyr::ldply(function(x, name){
		y <- read.csv(x) 
		info <- basename(x) %>% 
			stringr::str_sub(end = -5) %>% 
			stringr::str_split("_") %>% 
			unlist()
		y %>%
			dplyr::mutate(net = info[[1]],
										type = info[2],
										keep = info[3])
	})

link_redundancy %>%
	dplyr::mutate(type = interaction(type, keep)) %>%
	dplyr::group_by(net, type, robustness) %>%
	dplyr::summarise(n = n()) %>%
	tidyr::spread(robustness, n) %>%
	dplyr::mutate(critical = replace(critical, is.na(critical), 0),
								ordinary = replace(ordinary, is.na(ordinary), 0)) %>%
	dplyr::filter(type == "AB.A") %>%
	dplyr::inner_join(inv) %>%
	ggplot(aes(x = ordinary, z = redundant, y = critical)) +
	geom_point(aes(fill = inv), shape = 21, size = 5, alpha = 0.7) + 
	coord_tern() + 
	scale_fill_brewer(palette = "Set1")
```
